# preparation

## Install packages

Install the following packages if you have not.

```{r, eval = FALSE}
install.install.packages("usethis")
install.install.packages("devtools")
```

## Load packages

```{r}
library(devtools)
library(usethis)
```

# Build the package

## Pick the license

Here, we use the MIT license. See other license types [here](https://usethis.r-lib.org/reference/licenses.html).

```{r}
usethis::use_mit_license()
```

This will add a **License: ...** line in the **DESCRIPTION** file.

## Create data-raw folder to store raw datasets 

If you are creating datasets from raw datasets that are obtained externally, you can store them in a folder called **data_raw**, which is created by running the following code. Running the code also generates a file named **DATASET.R**.

```{r}
usethis::use_data_raw()
```

In this example package, I stored **sample_data.csv** in **data-raw**, which will be used later in generating a dataset that is going to be part of this data package.

## Create datasets

Inside **DATASET.R**, you can write R codes to generate datasets. But, you do not really have to use this file. You can just create a new one for this purpose. Here, I will create a file named **gen_data.qmd** under the **data-raw** folder. Go visit the file and come back here once you are done creating a dataset there.

## Create (update) documentation

```{r}
devtools::document()
```

## Check

```{r}
devtools::load_all()
data(sample_data_sf)
```